Score-based tests of measurement invariance: Use in practice

### 2014-01-30 frontiers/frontiers.Rnw
update one question about the motivation for intercept.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@310 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

To examine these issues, we generated data from a
two-factor model with three indicators each (see Figure~\ref{fig:path}).
The measurement invariance
violation occurred in one of four places: the factor loading associated with Scale 1 
 ($\lambda_{11}$), the unique variance  ($\psi_{11}$)
 or intercept associated with Scale 1 ($\mu_{11}$)
, the factor covariance ($\phi_{12}$).  Note that the
 latter violation is not necessarily a measurement invariance
 violation, but it is still a parameter instability that can occur in
 this type of model.
 We then tested for measurement invariance (parameter instability) in
 seven subsets of parameters: each of the four
individual parameters noted above, all six factor loadings, % $\lambda_{11}--\lambda_{62}$, and 
all six unique variances and all six intercepts. % $\epsilon_{11}--\epsilon_{66}$.

>>>>

To examine these issues, we generated data from a
two-factor model with three indicators each (see Figure~\ref{fig:path}).
The measurement invariance
violation occurred in one of four places: the factor loading associated with Scale 1 
 ($\lambda_{11}$), the unique variance  ($\psi_{11}$)
 or intercept associated with Scale 1 ($\mu_{11}$)
, the factor covariance ($\phi_{12}$).  Note that the
 latter violation is not necessarily a measurement invariance
 violation\seeme{need Meridith reference?}, but it is still a parameter instability that can occur in
 this type of model.
 We then tested for measurement invariance (parameter instability) in
 seven subsets of parameters: each of the four
individual parameters noted above, all six factor loadings, % $\lambda_{11}--\lambda_{62}$, and 
all six unique variances and all six intercepts. % $\epsilon_{11}--\epsilon_{66}$.
